Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-09-20 manuscript.Rmd

# Load data files
load("./Data/HistoricalDatabase.RData")
hodge.df <- readLines("./Data/hodge.txt", n = -1)
scopus.df <- read.csv("./Data/scopus.csv")
abb.df <- read.csv("./Data/master.csv")
sangam.df <- read.csv("./Data/sangam.csv")

@@

>>>>

# Load data files
load("./Data/HistoricalDatabase.RData")
hodge.df <- readLines("./Data/hodge.txt", n = -1)
scopus.df <- read.csv("./Data/scopus.csv")
abb.df <- read.csv("./Data/master.csv")
sangam.df <- read.csv("./Data/sangam.csv")
proquest_summary.df <- read.csv("./Data/proquest_summary.csv")

@@

```{r}

library(lubridate)
head(proquest_summary.df)
pq_summary <- proquest_summary.df

pq_summaryas.character(pq_summary$Citation.First)

  ifelse(proquest_summary.df$Citation.First == "Current", "9/19/15", proquest_summary.df$Citation.First)

proquest_summary.df$Citation.Last <- ifelse(proquest_summary.df$Abstract.Last == "Current", "9/19/15", proquest_summary.df$Citation.Last)
